\chapter{Literature Review}
This chapter introduces some existing document management system.
Section \ref{dms-features} gives lists of required features of \dms.
Section \ref{relate-works} explores some existing document management applications.

\section{Integrated features} \label{dms-features}
The features of \dms contains the following
\begin{description}
\item[Search file-reference]
User can search documents and their dependencies based on these keywords
\begin{enumerate}
\item Title
\item Description
\item Author's name
\item Date
\item Category
\end{enumerate}

\item[Upload/download file]
\item[Print documents]
\item[Generate ID and version of each document]
\item[Provide document's status]
\end{description}

\section{Related Works} \label{relate-works}
We pick 9 existing document management applications to investigate.
Each application has its interesting functionalities and characteristics.
We focus mainly on these 2 features, access control and document retention.
\begin{description}
\item[Alfresco One] \hfill \\
Alfresco One allows organizations to manage any type of content from small office documents, photographs, to large video files.
The system allows users to choose how to access their content --- via the Web, desktop or email --- while the server enforces access controls and security.

\item[Dockmee] \hfill \\
Dokmee has multiple editions targeted at companies of all sizes.
It can run in a Windows-based Intranet network, as a Web-hosted system or as a software-as-a-service model.
User can organize files into folders and can store unlimited number of files.

\item[Asite Document Manager] \hfill \\
Asite Document Manager provides an organization with a centralize storage with folder-like structure.
They claim that doing so saves user's time and effort of each party managing their own filing system.

\item[Eclipse Document Managment] \hfill \\
This program, developed by docSTAR, offers solution on storing and scanning electronic document files.
User can grant access to documents based on user permission.
It has a centralized storage accessible from other locations.
It searches documents by text, field, annotaion, and name with auto-complete feature.
The program also claims that it can locate documents that sound similar too.

\item[eFileCabinet] \hfill \\
eFileCabinet hosts document on their cloud server.
It searches document by filename and tags.
The program saves search history everytime user perform a search for autocompletion.
It can look for word and phrases inside a document.
User can sends document directly to eFileCabinet from Windows File Explorer or Microsoft Office Products.

\item[Contentverse] \hfill \\
Contentverse has file naming and storing familiar to cabinet and folder structure, indexed for immediate full-text search and retrieval.
The program track every changes -- every version of any file available for reference.
The program allows user to assign permission to users based on their specific job requirements.

\item[SmartFile] \hfill \\
SmartFile is a file management solution that enables everyone to more securely share, manage and control files offline and online.
SmartFile offers \gls{OCR} search.
User can find content within their documents.
The program narrows search result by let user specifiy date interval and file size interval.
User can view PDFs, JPG, PNG, GIF, and other image formats with its own viewer.
The characteristics of this program is its permanent activity logs.
Activity logs contain file's access information, who access the file, what user did to the file.
These logs are kept in the program permanently.


\end{description}